---
title: "**Data**"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Sequence data

All sequence data generated within this study can be obtained via the BioProject accession number [PRJNA809118](https://www.ncbi.nlm.nih.gov/bioproject/PRJNA809118). The dataset contains 30 samples from eggs, larvae, pupae, and adults of the black soldier fly sequenced with bacteria and fungi-specific primers.

<br/>

## Metadata

This table provides all metadata used in this study.

```{r metadata table, echo=F, warning=F, message=F}
library(reactable)
library(htmltools)
library(fontawesome)
library(dplyr)

metadata <- read.csv("data/metadata.csv", sep = ";") %>% 
  mutate(Biomass = format(round(Biomass, 3), nsmall = 3))

htmltools::browsable(
   tagList(
    tags$hr("aria-hidden" = "false"),
    tags$button("Download as CSV", onclick = "Reactable.downloadDataCSV('metadata-table', 'metadata.csv')"),
    
    reactable(
      metadata,
      elementId = "metadata-table",
      highlight = T,
      borderless = T,
      defaultPageSize = 10,
      resizable = T,
      searchable = T,
      compact = TRUE,
      wrap = F,
      showPageSizeOptions = T,
      pageSizeOptions = c(10, 25, 50, 100),
      columns = list(
        SampleID = colDef(
          style = list(position = "sticky", left = 0, background = "#f7f7f7", zIndex = 1, borderRight = "1px solid #eee"),
          headerStyle = list(position = "sticky", left = 0, background = "#f7f7f7", zIndex = 1, borderRight = "1px solid #eee")
          )
        ),
      theme = reactableTheme(
        rowSelectedStyle = list(backgroundColor = "#eee", boxShadow = "#f7f7f7")
        ),
      )
    )
  )
```

<br/>

## Explanation of metadata variables

This table provides an explanation of the variables presented in the metadata table.

```{r variable description, echo=F, warning=F}
variables <- read.csv("data/variables.csv", sep = ";")

reactable(
  variables, pagination = F,
  borderless = T,
  compact = T,
  columns = list(
    Variable = colDef(maxWidth = 170),
    Description = colDef(maxWidth = 550),
    Format = colDef(maxWidth = 100)
  )
)

```

